---
title: "Bank Lending Survey Chartpack"
author: "Aurelio Nocera"
date: "`r format(Sys.time(),'%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align='center',echo = FALSE,warning = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

```

The **Euro Area Bank Lending Survey (BLS)** provides information on bank lending conditions in the euro area. 
It supplements existing statistics with information on the *supply of, and demand for, loans to enterprises and households*. The BLS provides input to the assessment of monetary and economic developments carried out by the Governing Council of the European Central Bank (ECB), which feeds into the monetary policy decision-making process.

The BLS is conducted four times a year. 
It is usually published in January, April, July and October.

(**Source: ECB Website** [link](https://www.ecb.europa.eu/stats/ecb_surveys/bank_lending_survey/html/index.en.html))

```{r}
## Packages loading 
require("ecb")
require("data.table")
require("tidyr")
require("purrr")
require("dplyr")
require("xlsx")
require("zoo")
require("ggplot2")
require("glue")
require("httr")
require("curl")
require("lubridate")
require("plotly")

# List of countries that now belong to the Euro Area, including EuroArea reference "U2"
ea = c("AT", "BE", "CY", "DE", "EE", "HR","IE", "FR", "GR", "IT", "LT", "LV", 
       "LU", "SI", "SK", "FI", "NL", "ES", "PT", "U2", "MT")

date_convert = function(data){
  data = data %>%
    mutate(date = as_date(as.yearqtr(df$obstime, format = "%Y-Q%q")))
  return(data)
}

```

# Section 1 Firms 

## SubSection 1.1: Credit Standards (Q2 2024)

### Euro Area, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.U2.ALL..E.Z..ST.S.WFNET"
df<- ecb::get_data(series_key)

bls_firm_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]
bls_firm_cstd = date_convert(bls_firm_cstd)

bls_firm_cstd= bls_firm_cstd%>%
  filter(bls_item=="O")%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_firm_cstd,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Euro Area, Credit Standards/Firms, full time series")+
  theme_bw()

```

### Euro Area, breakdown (Q2 2024)

```{r}

series_key <- "BLS.Q.U2.ALL..E.Z..ST.S.WFNET"
df<- ecb::get_data(series_key)

bls_firm_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]
bls_firm_cstd = date_convert(bls_firm_cstd)

bls_firm_cstd1= bls_firm_cstd%>%
  filter(bls_item=="O")%>%
  mutate(Date=date-months(3))%>%
  select(Date,time_horizon,obsvalue)%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  filter(Date>="2020-01-01")

factors = c("BC", "CP", "GEA", "IFO", "LP", "MF", "MFC", "NBC", "RCD", "RTO")

bls_firm_cstd = bls_firm_cstd  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, CP, na.rm = T)/3, 
         "Risk perceptions" = sum(GEA, RCD, IFO, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, MFC, na.rm = T)/3, 
         "Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "RCD", "IFO", "NBC", "BC", "MFC", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))

bls_firm_cstd<-bls_firm_cstd%>%
  mutate(Factors=bls_item)%>%
  select(Date,Factors,value)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_firm_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_firm_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Euro Area, Credit Standards/Firms, breakdown factors, full time series")+
  theme_bw()

```

### France, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.FR.ALL..E.Z..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_firm_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]
bls_firm_cstd = date_convert(bls_firm_cstd)

bls_firm_cstd= bls_firm_cstd%>%
  filter(bls_item=="O")%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_firm_cstd,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("France, Credit Standards/Firms, full time series")+
  theme_bw()

```

### France, breakdown (Q2 2024)

```{r}

series_key <- "BLS.Q.FR.ALL..E.Z..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_firm_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]
bls_firm_cstd = date_convert(bls_firm_cstd)

bls_firm_cstd1= bls_firm_cstd%>%
  filter(bls_item=="O")%>%
  mutate(Date=date-months(3))%>%
  select(Date,time_horizon,obsvalue)%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  filter(Date>="2020-01-01")

factors = c("BC", "CP", "GEA", "IFO", "LP", "MF", "MFC", "NBC", "RCD", "RTO")

bls_firm_cstd = bls_firm_cstd  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, CP, na.rm = T)/3, 
         "Risk perceptions" = sum(GEA, RCD, IFO, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, MFC, na.rm = T)/3, 
         "Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "RCD", "IFO", "NBC", "BC", "MFC", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))

bls_firm_cstd<-bls_firm_cstd%>%
  mutate(Factors=bls_item)%>%
  select(Date,Factors,value)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_firm_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_firm_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("France, Credit Standards/Firms, breakdown factors, full time series")+
  theme_bw()

```


### Germany, full series (Q2 2024) 

```{r}

series_key <- "BLS.Q.DE.ALL..E.Z..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_firm_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]
bls_firm_cstd = date_convert(bls_firm_cstd)

bls_firm_cstd= bls_firm_cstd%>%
  filter(bls_item=="O")%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_firm_cstd,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Germany, Credit Standards/Firms, full time series")+
  theme_bw()

```

### Germany, breakdown (Q2 2024)

```{r}

series_key <- "BLS.Q.DE.ALL..E.Z..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_firm_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]
bls_firm_cstd = date_convert(bls_firm_cstd)

bls_firm_cstd1= bls_firm_cstd%>%
  filter(bls_item=="O")%>%
  mutate(Date=date-months(3))%>%
  select(Date,time_horizon,obsvalue)%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  filter(Date>="2020-01-01")

factors = c("BC", "CP", "GEA", "IFO", "LP", "MF", "MFC", "NBC", "RCD", "RTO")

bls_firm_cstd = bls_firm_cstd  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, CP, na.rm = T)/3, 
         "Risk perceptions" = sum(GEA, RCD, IFO, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, MFC, na.rm = T)/3, 
         "Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "RCD", "IFO", "NBC", "BC", "MFC", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))

bls_firm_cstd<-bls_firm_cstd%>%
  mutate(Factors=bls_item)%>%
  select(Date,Factors,value)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_firm_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_firm_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Germany, Credit Standards/Firms, breakdown factors, full time series")+
  theme_bw()

```

### Italy, full series (Q2 2024) 

```{r}

series_key <- "BLS.Q.IT.ALL..E.Z..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_firm_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]
bls_firm_cstd = date_convert(bls_firm_cstd)

bls_firm_cstd= bls_firm_cstd%>%
  filter(bls_item=="O")%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_firm_cstd,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Italy, Credit Standards/Firms, full time series")+
  theme_bw()

```

### Italy, breakdown (Q2 2024)

```{r}

series_key <- "BLS.Q.IT.ALL..E.Z..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_firm_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]
bls_firm_cstd = date_convert(bls_firm_cstd)

bls_firm_cstd1= bls_firm_cstd%>%
  filter(bls_item=="O")%>%
  mutate(Date=date-months(3))%>%
  select(Date,time_horizon,obsvalue)%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  filter(Date>="2020-01-01")

factors = c("BC", "CP", "GEA", "IFO", "LP", "MF", "MFC", "NBC", "RCD", "RTO")

bls_firm_cstd = bls_firm_cstd  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, CP, na.rm = T)/3, 
         "Risk perceptions" = sum(GEA, RCD, IFO, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, MFC, na.rm = T)/3, 
         "Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "RCD", "IFO", "NBC", "BC", "MFC", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))

bls_firm_cstd<-bls_firm_cstd%>%
  mutate(Factors=bls_item)%>%
  select(Date,Factors,value)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_firm_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_firm_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Italy, Credit Standards/Firms, breakdown factors, full time series")+
  theme_bw()

```


### Spain, full series (Q2 2024) 

```{r}

series_key <- "BLS.Q.ES.ALL..E.Z..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_firm_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]
bls_firm_cstd = date_convert(bls_firm_cstd)

bls_firm_cstd= bls_firm_cstd%>%
  filter(bls_item=="O")%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_firm_cstd,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Spain, Credit Standards/Firms, full time series")+
  theme_bw()

```

### Spain, breakdown (Q2 2024)

```{r}

series_key <- "BLS.Q.ES.ALL..E.Z..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_firm_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]
bls_firm_cstd = date_convert(bls_firm_cstd)

bls_firm_cstd1= bls_firm_cstd%>%
  filter(bls_item=="O")%>%
  mutate(Date=date-months(3))%>%
  select(Date,time_horizon,obsvalue)%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  filter(Date>="2020-01-01")

factors = c("BC", "CP", "GEA", "IFO", "LP", "MF", "MFC", "NBC", "RCD", "RTO")

bls_firm_cstd = bls_firm_cstd  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, CP, na.rm = T)/3, 
         "Risk perceptions" = sum(GEA, RCD, IFO, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, MFC, na.rm = T)/3, 
         "Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "RCD", "IFO", "NBC", "BC", "MFC", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))

bls_firm_cstd<-bls_firm_cstd%>%
  mutate(Factors=bls_item)%>%
  select(Date,Factors,value)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_firm_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_firm_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Spain, Credit Standards/Firms, breakdown factors, full time series")

```


## SubSection 1.2 Credit standards - SME loans

### Euro Area, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.U2.ALL.SME.E.Z..ST.S.WFNET"
df<- ecb::get_data(series_key)

bls_sme_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_sme_cstd = date_convert(bls_sme_cstd)

bls_sme_cstd= bls_sme_cstd%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_sme_cstd,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Euro Area, Credit Standards/SME firms, full time series")+
  theme_bw()

```

### Euro Area, breakdown (Q2 2024) 

```{r}

series_key<- "BLS.Q.U2.ALL.SME.E.Z..ST.S.WFNET"
df<- ecb::get_data(series_key)

bls_sme_cstd1= df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_sme_cstd1= date_convert(bls_sme_cstd1)

bls_sme_cstd1= bls_sme_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)%>%
  filter(Date>="2020-01-01")

series_key<- "BLS.Q.U2.ALL..E.SME.B3.ST.S.WFNET"
df<- ecb::get_data(series_key)

bls_sme_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_sme_cstd = date_convert(bls_sme_cstd)

factors = c("BC", "CP", "GEA", "IFO", "LP", "MF", "MFC", "NBC", "RCD", "RTO")

bls_sme_cstd = bls_sme_cstd  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, CP, na.rm = T)/3, 
         "Risk perceptions" = sum(GEA, RCD, IFO, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, MFC, na.rm = T)/3, 
         "Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "RCD", "IFO", "NBC", "BC", "MFC", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))

bls_sme_cstd<-bls_sme_cstd%>%
  mutate(Factors=bls_item)%>%
  select(Date,Factors,value)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_sme_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_sme_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Euro Area, Credit Standards/SME Firms, breakdown factors, full time series")

```

### France, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.FR.ALL.SME.E.Z..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_sme_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_sme_cstd1 = date_convert(bls_sme_cstd1)

bls_sme_cstd1= bls_sme_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_sme_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("France, Credit Standards/SME Firms, full time series")+
  theme_bw()

```

### France,breakdown (Q2 2024)

```{r}

series_key<- "BLS.Q.FR.ALL..E.SME.B3.ST.S.FNET"
df<- ecb::get_data(series_key)

bls_sme_st = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_sme_st = date_convert(bls_sme_st)

factors = c("BC", "CP", "GEA", "IFO", "LP", "MF", "MFC", "NBC", "RCD", "RTO")

bls_sme_st = bls_sme_st  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, CP, na.rm = T)/3, 
         "Risk perceptions" = sum(GEA, RCD, IFO, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, MFC, na.rm = T)/3, 
         "Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "RCD", "IFO", "NBC", "BC", "MFC", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

bls_sme_cstd1<-bls_sme_cstd1%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_sme_st,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_sme_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("France, Credit Standards/SME Firms, breakdown factors, full time series")

```

### Germany, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.DE.ALL.SME.E.Z..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_sme_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_sme_cstd1 = date_convert(bls_sme_cstd1)

bls_sme_cstd1= bls_sme_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_sme_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Germany, Credit Standards/SME Firms, full time series")+
  theme_bw()

```

### Germany,breakdown (Q2 2024)

```{r}

series_key<- "BLS.Q.DE.ALL..E.SME.B3.ST.S.FNET"
df<- ecb::get_data(series_key)

bls_sme_st = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_sme_st = date_convert(bls_sme_st)

factors = c("BC", "CP", "GEA", "IFO", "LP", "MF", "MFC", "NBC", "RCD", "RTO")

bls_sme_st = bls_sme_st  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, CP, na.rm = T)/3, 
         "Risk perceptions" = sum(GEA, RCD, IFO, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, MFC, na.rm = T)/3, 
         "Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "RCD", "IFO", "NBC", "BC", "MFC", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

bls_sme_cstd1<-bls_sme_cstd1%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_sme_st,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_sme_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Germany, Credit Standards/SME Firms, breakdown factors, full time series")

```
### Italy, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.IT.ALL.SME.E.Z..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_sme_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_sme_cstd1 = date_convert(bls_sme_cstd1)

bls_sme_cstd1= bls_sme_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_sme_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Italy, Credit Standards/SME Firms, full time series")+
  theme_bw()

```

### Italy,breakdown (Q2 2024)

```{r}

series_key<- "BLS.Q.IT.ALL..E.SME.B3.ST.S.FNET"
df<- ecb::get_data(series_key)

bls_sme_st = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_sme_st = date_convert(bls_sme_st)

factors = c("BC", "CP", "GEA", "IFO", "LP", "MF", "MFC", "NBC", "RCD", "RTO")

bls_sme_st = bls_sme_st  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, CP, na.rm = T)/3, 
         "Risk perceptions" = sum(GEA, RCD, IFO, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, MFC, na.rm = T)/3, 
         "Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "RCD", "IFO", "NBC", "BC", "MFC", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

bls_sme_cstd1<-bls_sme_cstd1%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_sme_st,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_sme_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Italy, Credit Standards/SME Firms, breakdown factors, full time series")

```

### Spain, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.ES.ALL.SME.E.Z..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_sme_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_sme_cstd = date_convert(bls_sme_cstd)

bls_sme_cstd= bls_sme_cstd%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_sme_cstd,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Spain, Credit Standards/SME Firms, full time series")+
  theme_bw()

```

### Spain,breakdown (Q2 2024)

```{r}

series_key<- "BLS.Q.ES.ALL..E.SME.B3.ST.S.FNET"
df<- ecb::get_data(series_key)

bls_sme_st = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_sme_st = date_convert(bls_sme_st)

factors = c("BC", "CP", "GEA", "IFO", "LP", "MF", "MFC", "NBC", "RCD", "RTO")

bls_sme_st = bls_sme_st  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, CP, na.rm = T)/3, 
         "Risk perceptions" = sum(GEA, RCD, IFO, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, MFC, na.rm = T)/3, 
         "Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "RCD", "IFO", "NBC", "BC", "MFC", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

bls_sme_cstd1<-bls_sme_cstd1%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_sme_st,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_sme_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Spain, Credit Standards/SME Firms, breakdown factors, full time series")

```

## SubSection 1.3 Credit standards - LE loans (Q2 2024)

### Euro Area, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.U2.ALL.LE.E.Z..ST.S.WFNET"
df<- ecb::get_data(series_key)

bls_le_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_le_cstd = date_convert(bls_le_cstd)

bls_le_cstd= bls_le_cstd%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_le_cstd,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Euro Area, Credit Standards/Large firms, full time series")+
  theme_bw()

```

### Euro Area, breakdown (Q2 2024) 

```{r}

series_key<- "BLS.Q.U2.ALL.LE.E.Z..ST.S.WFNET"
df<- ecb::get_data(series_key)

bls_le_cstd1= df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_le_cstd1= date_convert(bls_le_cstd1)

bls_le_cstd1= bls_le_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)%>%
  filter(Date>="2020-01-01")

series_key<- "BLS.Q.U2.ALL..E.LE.B3.ST.S.WFNET"
df<- ecb::get_data(series_key)

bls_le_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_le_cstd = date_convert(bls_le_cstd)

factors = c("BC", "CP", "GEA", "IFO", "LP", "MF", "MFC", "NBC", "RCD", "RTO")

bls_le_cstd = bls_le_cstd  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, CP, na.rm = T)/3, 
         "Risk perceptions" = sum(GEA, RCD, IFO, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, MFC, na.rm = T)/3, 
         "Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "RCD", "IFO", "NBC", "BC", "MFC", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))

bls_le_cstd<-bls_le_cstd%>%
  mutate(Factors=bls_item)%>%
  select(Date,Factors,value)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_le_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_le_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Euro Area, Credit Standards/Large Firms, breakdown factors, full time series")

```

###France, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.FR.ALL.LE.E.Z..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_le_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_le_cstd1 = date_convert(bls_le_cstd1)

bls_le_cstd1= bls_le_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_le_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("France, Credit Standards/Large Firms, full time series")+
  theme_bw()

```

###France,breakdown (Q2 2024)

```{r}

series_key<- "BLS.Q.FR.ALL..E.LE.B3.ST.S.FNET"
df<- ecb::get_data(series_key)

bls_le_st = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_le_st = date_convert(bls_le_st)

factors = c("BC", "CP", "GEA", "IFO", "LP", "MF", "MFC", "NBC", "RCD", "RTO")

bls_le_st = bls_le_st  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, CP, na.rm = T)/3, 
         "Risk perceptions" = sum(GEA, RCD, IFO, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, MFC, na.rm = T)/3, 
         "Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "RCD", "IFO", "NBC", "BC", "MFC", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

bls_le_cstd1<-bls_le_cstd1%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_le_st,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_le_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("France, Credit Standards/Large Firms, breakdown factors, full time series")

```

### Germany, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.DE.ALL.LE.E.Z..ST.S.FNET"

bls_le_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_le_cstd1 = date_convert(bls_le_cstd1)

bls_le_cstd1= bls_le_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_le_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Germany, Credit Standards/Large Firms, full time series")+
  theme_bw()

```

### Germany,breakdown (Q2 2024)

```{r}

series_key<- "BLS.Q.DE.ALL..E.LE.B3.ST.S.FNET"
df<- ecb::get_data(series_key)

bls_le_st = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_le_st = date_convert(bls_le_st)

factors = c("BC", "CP", "GEA", "IFO", "LP", "MF", "MFC", "NBC", "RCD", "RTO")

bls_le_st = bls_le_st  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, CP, na.rm = T)/3, 
         "Risk perceptions" = sum(GEA, RCD, IFO, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, MFC, na.rm = T)/3, 
         "Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "RCD", "IFO", "NBC", "BC", "MFC", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

bls_le_cstd1<-bls_le_cstd1%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_le_st,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_le_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Germany, Credit Standards/Large Firms, breakdown factors, full time series")

```

### Italy, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.IT.ALL.LE.E.Z..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_le_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_le_cstd1 = date_convert(bls_le_cstd1)

bls_le_cstd1= bls_le_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_le_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Italy, Credit Standards/Large Firms, full time series")+
  theme_bw()

```

### Italy,breakdown (Q2 2024)

```{r}

series_key<- "BLS.Q.IT.ALL..E.LE.B3.ST.S.FNET"
df<- ecb::get_data(series_key)

bls_le_st = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_le_st = date_convert(bls_le_st)

factors = c("BC", "CP", "GEA", "IFO", "LP", "MF", "MFC", "NBC", "RCD", "RTO")

bls_le_st = bls_le_st  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, CP, na.rm = T)/3, 
         "Risk perceptions" = sum(GEA, RCD, IFO, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, MFC, na.rm = T)/3, 
         "Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "RCD", "IFO", "NBC", "BC", "MFC", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

bls_le_cstd1<-bls_le_cstd1%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_le_st,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_le_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Italy, Credit Standards/Large Firms, breakdown factors, full time series")

```

### Spain, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.ES.ALL.LE.E.Z..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_le_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_le_cstd1 = date_convert(bls_le_cstd1)

bls_le_cstd1= bls_le_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_le_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Spain, Credit Standards/Large Firms, full time series")+
  theme_bw()

```

### Spain,breakdown (Q2 2024)

```{r}

series_key<- "BLS.Q.ES.ALL..E.LE.B3.ST.S.FNET"
df<- ecb::get_data(series_key)

bls_le_st = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_le_st = date_convert(bls_le_st)

factors = c("BC", "CP", "GEA", "IFO", "LP", "MF", "MFC", "NBC", "RCD", "RTO")

bls_le_st = bls_le_st  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, CP, na.rm = T)/3, 
         "Risk perceptions" = sum(GEA, RCD, IFO, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, MFC, na.rm = T)/3, 
         "Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "RCD", "IFO", "NBC", "BC", "MFC", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

bls_le_cstd1<-bls_le_cstd1%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_le_st,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_le_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Spain, Credit Standards/Large Firms, breakdown factors, full time series")

```
## Subsection 1.4 Demand

### Euro Area, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.U2.ALL.O.E.Z..ZZ.D.WFNET"
df<- ecb::get_data(series_key)

bls_firm_demand1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand1 = date_convert(bls_firm_demand1)

bls_firm_demand1= bls_firm_demand1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_firm_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Euro Area, Firms/ Loan Demand, full time series")+
  theme_bw()

```

### Euro Area, breakdown (Q2 2024)

```{r}

# DEMAND/ ENTERPRISES - EURO AREA, "U2"

bls_firm_demand1<-bls_firm_demand1%>%
    filter(Date>="2020-01-01")

series_key <- "BLS.Q.U2.ALL..E.Z..ZZ.D.WFNET"
df<- ecb::get_data(series_key)

bls_firm_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand = date_convert(bls_firm_demand)

factors = c("O", "DR", "DSI", "EQI", "FIX", "GLI", "IF", "INV", "LNB", "LOB", "MAA")

bls_firm_demand = bls_firm_demand  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Other financing needs" = sum(DR,MAA, na.rm = T)/2, 
         "Use of alternative finance" = sum(IF, LOB, LNB, DSI, EQI, na.rm = T)/5, 
         "Fixed Investment" = (FIX),
         "Inventories and Working Capital"=(INV),
         "General level of interest rate"=(GLI)) %>%
  select(-c("DR", "DSI", "EQI", "FIX", "GLI", "IF", "INV", "LNB", "LOB", "MAA")) %>%
  gather(key = "bls_item", val = "value", -c("O",  "time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_firm_demand,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_firm_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Euro Area, Firms/ Loan demand, breakdown factors, full time series")

```

### France, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.FR.ALL.O.E.Z..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_firm_demand1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]
bls_firm_demand1 = date_convert(bls_firm_demand1)

bls_firm_demand1= bls_firm_demand1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_firm_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("France, Firms/ Demand, full time series")+
  theme_bw()

```

### France, breakdown (Q2 2024)

```{r}

# DEMAND/ ENTERPRISES - EURO AREA, "U2"

bls_firm_demand1<-bls_firm_demand1%>%
    filter(Date>="2020-01-01")

series_key <- "BLS.Q.FR.ALL..E.Z..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_firm_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand = date_convert(bls_firm_demand)

factors = c("O", "DR", "DSI", "EQI", "FIX", "GLI", "IF", "INV", "LNB", "LOB", "MAA")

bls_firm_demand = bls_firm_demand  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Other financing needs" = sum(DR,MAA, na.rm = T)/2, 
         "Use of alternative finance" = sum(IF, LOB, LNB, DSI, EQI, na.rm = T)/5, 
         "Fixed Investment" = (FIX),
         "Inventories and Working Capital"=(INV),
         "General level of interest rate"=(GLI)) %>%
  select(-c("DR", "DSI", "EQI", "FIX", "GLI", "IF", "INV", "LNB", "LOB", "MAA")) %>%
  gather(key = "bls_item", val = "value", -c("O",  "time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_firm_demand,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_firm_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("France, Firms/Demand, breakdown factors, full time series")

```

### Germany, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.DE.ALL.O.E.Z..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_firm_demand1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand1 = date_convert(bls_firm_demand1)

bls_firm_demand1= bls_firm_demand1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_firm_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Germany, Firms/Demand, full time series")+
  theme_bw()

```

### Germany, breakdown (Q2 2024)

```{r}

# DEMAND/ ENTERPRISES - EURO AREA, "U2"

bls_firm_demand1<-bls_firm_demand1%>%
    filter(Date>="2020-01-01")

series_key <- "BLS.Q.DE.ALL..E.Z..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_firm_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand = date_convert(bls_firm_demand)

factors = c("O", "DR", "DSI", "EQI", "FIX", "GLI", "IF", "INV", "LNB", "LOB", "MAA")

bls_firm_demand = bls_firm_demand  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Other financing needs" = sum(DR,MAA, na.rm = T)/2, 
         "Use of alternative finance" = sum(IF, LOB, LNB, DSI, EQI, na.rm = T)/5, 
         "Fixed Investment" = (FIX),
         "Inventories and Working Capital"=(INV),
         "General level of interest rate"=(GLI)) %>%
  select(-c("DR", "DSI", "EQI", "FIX", "GLI", "IF", "INV", "LNB", "LOB", "MAA")) %>%
  gather(key = "bls_item", val = "value", -c("O",  "time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_firm_demand,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_firm_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Germany, Firms/Demand, breakdown factors, full time series")


```

### Italy, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.IT.ALL.O.E.Z..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_firm_demand1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand1 = date_convert(bls_firm_demand1)

bls_firm_demand1= bls_firm_demand1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_firm_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Italy, Firms/Demand, full time series")+
  theme_bw()

```

### Italy, breakdown (Q2 2024)

```{r}

# DEMAND/ ENTERPRISES - EURO AREA, "U2"

bls_firm_demand1<-bls_firm_demand1%>%
    filter(Date>="2020-01-01")

series_key <- "BLS.Q.IT.ALL..E.Z..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_firm_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand = date_convert(bls_firm_demand)

factors = c("O", "DR", "DSI", "EQI", "FIX", "GLI", "IF", "INV", "LNB", "LOB", "MAA")

bls_firm_demand = bls_firm_demand  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Other financing needs" = sum(DR,MAA, na.rm = T)/2, 
         "Use of alternative finance" = sum(IF, LOB, LNB, DSI, EQI, na.rm = T)/5, 
         "Fixed Investment" = (FIX),
         "Inventories and Working Capital"=(INV),
         "General level of interest rate"=(GLI)) %>%
  select(-c("DR", "DSI", "EQI", "FIX", "GLI", "IF", "INV", "LNB", "LOB", "MAA")) %>%
  gather(key = "bls_item", val = "value", -c("O",  "time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_firm_demand,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_firm_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Italy, Firms/Demand, breakdown factors, full time series")

```

### Spain, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.ES.ALL.O.E.Z..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_firm_demand1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand1 = date_convert(bls_firm_demand1)

bls_firm_demand1= bls_firm_demand1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_firm_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Spain, Firms/Demand, full time series")+
  theme_bw()

```

### Spain, breakdown (Q2 2024)

```{r}

# DEMAND/ ENTERPRISES - EURO AREA, "U2"

bls_firm_demand1<-bls_firm_demand1%>%
    filter(Date>="2020-01-01")

series_key <- "BLS.Q.ES.ALL..E.Z..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_firm_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand = date_convert(bls_firm_demand)

factors = c("O", "DR", "DSI", "EQI", "FIX", "GLI", "IF", "INV", "LNB", "LOB", "MAA")

bls_firm_demand = bls_firm_demand  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Other financing needs" = sum(DR,MAA, na.rm = T)/2, 
         "Use of alternative finance" = sum(IF, LOB, LNB, DSI, EQI, na.rm = T)/5, 
         "Fixed Investment" = (FIX),
         "Inventories and Working Capital"=(INV),
         "General level of interest rate"=(GLI)) %>%
  select(-c("DR", "DSI", "EQI", "FIX", "GLI", "IF", "INV", "LNB", "LOB", "MAA")) %>%
  gather(key = "bls_item", val = "value", -c("O",  "time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_firm_demand,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_firm_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Spain, Firms/Demand, breakdown factors, full time series")

```


## Subsection 1.5 Demand/ Type of loans, backward looking 

### Euro area, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.U2.ALL.LE+LTL+SME+STL.E.Z.B3.ZZ.D.WFNET"
df<- ecb::get_data(series_key)

bls_firm_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand = date_convert(bls_firm_demand)

bls_firm_demand= bls_firm_demand%>%
  mutate(Date=date-months(3))%>%
  mutate(TypeLoan=case_when(
    bls_item=="LE"~"Large Firms",
    bls_item=="SME"~"SME",
    bls_item=="LTL"~"Long term loans",
    bls_item=="STL"~"Short term loans"))%>%
  select(Date,TypeLoan,obsvalue)

ggplot(data=bls_firm_demand,aes(x=Date,y=obsvalue,group=TypeLoan))+
  geom_line(aes(color=TypeLoan))+
  scale_color_manual(values=c("red","black","green","purple"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Euro Area, Firms/ Demand -Type of Loans,Backward looking, full time series")+
  theme_bw()

```

### France, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.FR.ALL.LE+LTL+SME+STL.E.Z.B3.ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_firm_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand = date_convert(bls_firm_demand)

bls_firm_demand= bls_firm_demand%>%
  mutate(Date=date-months(3))%>%
  mutate(TypeLoan=case_when(
    bls_item=="LE"~"Large Firms",
    bls_item=="SME"~"SME",
    bls_item=="LTL"~"Long term loans",
    bls_item=="STL"~"Short term loans"))%>%
  select(Date,TypeLoan,obsvalue)

ggplot(data=bls_firm_demand,aes(x=Date,y=obsvalue,group=TypeLoan))+
  geom_line(aes(color=TypeLoan))+
  scale_color_manual(values=c("red","black","green","purple"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("France, Firms/ Demand - Type of Loans,Backward looking, full time series")+
  theme_bw()

```

### Germany, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.DE.ALL.LE+LTL+SME+STL.E.Z.B3.ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_firm_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand = date_convert(bls_firm_demand)

bls_firm_demand= bls_firm_demand%>%
  mutate(Date=date-months(3))%>%
  mutate(TypeLoan=case_when(
    bls_item=="LE"~"Large Firms",
    bls_item=="SME"~"SME",
    bls_item=="LTL"~"Long term loans",
    bls_item=="STL"~"Short term loans"))%>%
  select(Date,TypeLoan,obsvalue)

ggplot(data=bls_firm_demand,aes(x=Date,y=obsvalue,group=TypeLoan))+
  geom_line(aes(color=TypeLoan))+
  scale_color_manual(values=c("red","black","green","purple"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Germany, Firms/ Demand - Type of Loans,Backward looking, full time series")+
  theme_bw()

```

### Italy, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.IT.ALL.LE+LTL+SME+STL.E.Z.B3.ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_firm_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand = date_convert(bls_firm_demand)

bls_firm_demand= bls_firm_demand%>%
  mutate(Date=date-months(3))%>%
  mutate(TypeLoan=case_when(
    bls_item=="LE"~"Large Firms",
    bls_item=="SME"~"SME",
    bls_item=="LTL"~"Long term loans",
    bls_item=="STL"~"Short term loans"))%>%
  select(Date,TypeLoan,obsvalue)

ggplot(data=bls_firm_demand,aes(x=Date,y=obsvalue,group=TypeLoan))+
  geom_line(aes(color=TypeLoan))+
  scale_color_manual(values=c("red","black","green","purple"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Italy, Firms/ Demand - Type of Loans,Backward looking, full time series")+
  theme_bw()

```

### Spain, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.ES.ALL.LE+LTL+SME+STL.E.Z.B3.ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_firm_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand = date_convert(bls_firm_demand)

bls_firm_demand= bls_firm_demand%>%
  mutate(Date=date-months(3))%>%
  mutate(TypeLoan=case_when(
    bls_item=="LE"~"Large Firms",
    bls_item=="SME"~"SME",
    bls_item=="LTL"~"Long term loans",
    bls_item=="STL"~"Short term loans"))%>%
  select(Date,TypeLoan,obsvalue)

ggplot(data=bls_firm_demand,aes(x=Date,y=obsvalue,group=TypeLoan))+
  geom_line(aes(color=TypeLoan))+
  scale_color_manual(values=c("red","black","green","purple"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Spain, Firms/ Demand - Type of Loans,Backward looking, full time series")+
  theme_bw()

```

## Subsection 1.6 Demand/ Type of loans, forward looking 

### Euro area, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.U2.ALL.LE+LTL+SME+STL.E.Z.F3.ZZ.D.WFNET"
df<- ecb::get_data(series_key)

bls_firm_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand = date_convert(bls_firm_demand)

bls_firm_demand= bls_firm_demand%>%
  mutate(Date=date-months(3))%>%
  mutate(TypeLoan=case_when(
    bls_item=="LE"~"Large Firms",
    bls_item=="SME"~"SME",
    bls_item=="LTL"~"Long term loans",
    bls_item=="STL"~"Short term loans"))%>%
  select(Date,TypeLoan,obsvalue)

ggplot(data=bls_firm_demand,aes(x=Date,y=obsvalue,group=TypeLoan))+
  geom_line(aes(color=TypeLoan))+
  scale_color_manual(values=c("red","black","green","purple"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Euro Area, Firms/ Demand - Type of Loans,Forward looking, full time series")+
  theme_bw()

```

### France, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.FR.ALL.LE+LTL+SME+STL.E.Z.F3.ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_firm_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand = date_convert(bls_firm_demand)

bls_firm_demand= bls_firm_demand%>%
  mutate(Date=date-months(3))%>%
  mutate(TypeLoan=case_when(
    bls_item=="LE"~"Large Firms",
    bls_item=="SME"~"SME",
    bls_item=="LTL"~"Long term loans",
    bls_item=="STL"~"Short term loans"))%>%
  select(Date,TypeLoan,obsvalue)

ggplot(data=bls_firm_demand,aes(x=Date,y=obsvalue,group=TypeLoan))+
  geom_line(aes(color=TypeLoan))+
  scale_color_manual(values=c("red","black","green","purple"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("France, Firms/ Demand - Type of Loans,Forward looking, full time series")+
  theme_bw()

```

### Germany, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.DE.ALL.LE+LTL+SME+STL.E.Z.F3.ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_firm_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand = date_convert(bls_firm_demand)

bls_firm_demand= bls_firm_demand%>%
  mutate(Date=date-months(3))%>%
  mutate(TypeLoan=case_when(
    bls_item=="LE"~"Large Firms",
    bls_item=="SME"~"SME",
    bls_item=="LTL"~"Long term loans",
    bls_item=="STL"~"Short term loans"))%>%
  select(Date,TypeLoan,obsvalue)

ggplot(data=bls_firm_demand,aes(x=Date,y=obsvalue,group=TypeLoan))+
  geom_line(aes(color=TypeLoan))+
  scale_color_manual(values=c("red","black","green","purple"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Germany, Firms/ Demand - Type of Loans,Forward looking, full time series")+
  theme_bw()

```

### Italy, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.IT.ALL.LE+LTL+SME+STL.E.Z.F3.ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_firm_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand = date_convert(bls_firm_demand)

bls_firm_demand= bls_firm_demand%>%
  mutate(Date=date-months(3))%>%
  mutate(TypeLoan=case_when(
    bls_item=="LE"~"Large Firms",
    bls_item=="SME"~"SME",
    bls_item=="LTL"~"Long term loans",
    bls_item=="STL"~"Short term loans"))%>%
  select(Date,TypeLoan,obsvalue)

ggplot(data=bls_firm_demand,aes(x=Date,y=obsvalue,group=TypeLoan))+
  geom_line(aes(color=TypeLoan))+
  scale_color_manual(values=c("red","black","green","purple"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Italy, Firms/ Demand - Type of Loans,Forward looking, full time series")+
  theme_bw()

```

### Spain, full series (Q2 2024)

```{r}

series_key<- "BLS.Q.ES.ALL.LE+LTL+SME+STL.E.Z.F3.ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_firm_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_firm_demand = date_convert(bls_firm_demand)

bls_firm_demand= bls_firm_demand%>%
  mutate(Date=date-months(3))%>%
  mutate(TypeLoan=case_when(
    bls_item=="LE"~"Large Firms",
    bls_item=="SME"~"SME",
    bls_item=="LTL"~"Long term loans",
    bls_item=="STL"~"Short term loans"))%>%
  select(Date,TypeLoan,obsvalue)

ggplot(data=bls_firm_demand,aes(x=Date,y=obsvalue,group=TypeLoan))+
  geom_line(aes(color=TypeLoan))+
  scale_color_manual(values=c("red","black","green","purple"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Spain,Firms/ Demand - Type of Loans,Forward looking, full time series")+
  theme_bw()

```


# BLS - Households 
## Subsection 2.1 Credit Standards 

### Euro area, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.U2.ALL.Z.H.H..ST.S.WFNET"
df<- ecb::get_data(series_key)

bls_hh_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_cstd1 = date_convert(bls_hh_cstd1)

bls_hh_cstd1= bls_hh_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_hh_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Euro Area, Households/ Credit standards, full time series")+
  theme_bw()

```

### Euro Area, breakdown (Q2 2024)

```{r}

bls_hh_cstd1<- bls_hh_cstd1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.U2.ALL..H.H..ST.S.WFNET"
df<- ecb::get_data(series_key)

bls_hh_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_cstd = date_convert(bls_hh_cstd)

factors = c("Z", "BC", "BSC", "CP", "GEA", "CWB", "LP", "MF", "HMP", "NBC", "RTO")

bls_hh_cstd = bls_hh_cstd  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, BSC, CP, na.rm = T)/4, 
         "Risk perceptions" = sum(GEA, HMP, CWB, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, na.rm = T )/2, 
         "Banks' Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "BSC", "HMP", "NBC", "BC", "CWB", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("Z",  "time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_hh_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_hh_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Euro Area, Households Credit standards, breakdown factors, full time series")

```

### France, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.FR.ALL.Z.H.H..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_hh_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_cstd1 = date_convert(bls_hh_cstd1)

bls_hh_cstd1= bls_hh_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_hh_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("France, Households/ Credit standards, full time series")+
  theme_bw()

```

### France, breakdown(Q2 2024)

```{r}
# HOUSEHOLD CREDIT STANDARDS
# France 

bls_hh_cstd1<- bls_hh_cstd1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.FR.ALL..H.H..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_hh_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_cstd = date_convert(bls_hh_cstd)

factors = c("Z", "BC", "BSC", "CP", "GEA", "CWB", "LP", "MF", "HMP", "NBC", "RTO")

bls_hh_cstd = bls_hh_cstd  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, BSC, CP, na.rm = T)/4, 
         "Risk perceptions" = sum(GEA, HMP, CWB, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, na.rm = T )/2, 
         "Banks' Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "BSC", "HMP", "NBC", "BC", "CWB", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("Z",  "time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_hh_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_hh_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("France, Households Credit standards, breakdown factors, full time series")

```

### Germany, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.DE.ALL.Z.H.H..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_hh_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_cstd1 = date_convert(bls_hh_cstd1)

bls_hh_cstd1= bls_hh_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_hh_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Germany, Households/ Credit standards, full time series")+
  theme_bw()

```

### Germany, breakdown (Q2 2024)

```{r}
# HOUSEHOLD CREDIT STANDARDS
# Germany

bls_hh_cstd1<- bls_hh_cstd1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.DE.ALL..H.H..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_hh_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_cstd = date_convert(bls_hh_cstd)

factors = c("Z", "BC", "BSC", "CP", "GEA", "CWB", "LP", "MF", "HMP", "NBC", "RTO")

bls_hh_cstd = bls_hh_cstd  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, BSC, CP, na.rm = T)/4, 
         "Risk perceptions" = sum(GEA, HMP, CWB, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, na.rm = T )/2, 
         "Banks' Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "BSC", "HMP", "NBC", "BC", "CWB", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("Z",  "time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_hh_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_hh_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Germany, Households Credit standards, breakdown factors, full time series")

```

### Spain, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.ES.ALL.Z.H.H..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_hh_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_cstd1 = date_convert(bls_hh_cstd1)

bls_hh_cstd1= bls_hh_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_hh_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Spain, Households/ Credit standards, full time series")+
  theme_bw()

```

### Spain, breakdown (Q2 2024)

```{r}
# HOUSEHOLD CREDIT STANDARDS
# Spain

bls_hh_cstd1<- bls_hh_cstd1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.ES.ALL..H.H..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_hh_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_cstd = date_convert(bls_hh_cstd)

factors = c("Z", "BC", "BSC", "CP", "GEA", "CWB", "LP", "MF", "HMP", "NBC", "RTO")

bls_hh_cstd = bls_hh_cstd  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, BSC, CP, na.rm = T)/4, 
         "Risk perceptions" = sum(GEA, HMP, CWB, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, na.rm = T )/2, 
         "Banks' Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "BSC", "HMP", "NBC", "BC", "CWB", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("Z",  "time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_hh_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_hh_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Spain, Households Credit standards, breakdown factors, full time series")

```

### Italy, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.IT.ALL.Z.H.H..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_hh_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_cstd1 = date_convert(bls_hh_cstd1)

bls_hh_cstd1= bls_hh_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_hh_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Italy, Households/ Credit standards, full time series")+
  theme_bw()

```

### Italy, breakdown (Q2 2024)

```{r}

bls_hh_cstd1<- bls_hh_cstd1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.IT.ALL..H.H..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_hh_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_cstd = date_convert(bls_hh_cstd)

factors = c("Z", "BC", "BSC", "CP", "GEA", "CWB", "LP", "MF", "HMP", "NBC", "RTO")

bls_hh_cstd = bls_hh_cstd  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, BSC, CP, na.rm = T)/4, 
         "Risk perceptions" = sum(GEA, HMP, CWB, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, na.rm = T )/2, 
         "Banks' Risk tolerance" = (RTO)) %>%
  select(-c("LP", "MF", "CP", "GEA", "BSC", "HMP", "NBC", "BC", "CWB", "RTO")) %>%
  gather(key = "bls_item", val = "value", -c("Z",  "time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_hh_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_hh_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Italy, Households Credit standards, breakdown factors, full time series")

```

## Subsection 2.2 Demand for Mortgages 

### Euro area, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.U2.ALL.Z.H.H..ZZ.D.WFNET"
df<- ecb::get_data(series_key)

bls_hh_demand1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_demand1 = date_convert(bls_hh_demand1)

bls_hh_demand1= bls_hh_demand1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_hh_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Euro Area, Households/ Demand for mortgage, full time series")+
  theme_bw()

```

### Euro area, breakdown (Q2 2024)

```{r}

bls_hh_demand1<- bls_hh_demand1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.U2.ALL..H.H..ZZ.D.WFNET"
df<- ecb::get_data(series_key)

bls_hh_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_demand = date_convert(bls_hh_demand)

factors = c("Z","DR","RFR","IFS","LOB","OSF","GLI","HMP","CCF")

bls_hh_demand = bls_hh_demand  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Other financing needs" = sum(DR,RFR, na.rm = T)/2, 
         "Use of alternative finance" = sum(IFS, LOB, OSF, na.rm = T)/3, 
         "General Level of Interest Rate" = (GLI), 
         "Housing Market Prospects" = (HMP),
         "Consumer Confidence"=(CCF)) %>%
  select(-c("DR","RFR","IFS","LOB","OSF","GLI","HMP","CCF")) %>%
  gather(key = "bls_item", val = "value", -c("Z","time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_hh_demand,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_hh_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Euro Area, Households Credit standards, breakdown factors, full time series")

```

### France, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.FR.ALL.Z.H.H..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_hh_demand1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_demand1 = date_convert(bls_hh_demand1)

bls_hh_demand1= bls_hh_demand1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_hh_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("France, Households/ Demand for mortgage, full time series")+
  theme_bw()

```

### France, breakdown (Q2 2024)

```{r}

bls_hh_demand1<- bls_hh_demand1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.FR.ALL..H.H..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_hh_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_demand = date_convert(bls_hh_demand)

factors = c("Z","DR","RFR","IFS","LOB","OSF","GLI","HMP","CCF")

bls_hh_demand = bls_hh_demand  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Other financing needs" = sum(DR,RFR, na.rm = T)/2, 
         "Use of alternative finance" = sum(IFS, LOB, OSF, na.rm = T)/3, 
         "General Level of Interest Rate" = (GLI), 
         "Housing Market Prospects" = (HMP),
         "Consumer Confidence"=(CCF)) %>%
  select(-c("DR","RFR","IFS","LOB","OSF","GLI","HMP","CCF")) %>%
  gather(key = "bls_item", val = "value", -c("Z","time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_hh_demand,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_hh_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("France, Households Credit standards, breakdown factors, full time series")

```

### Germany, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.DE.ALL.Z.H.H..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_hh_demand1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_demand1 = date_convert(bls_hh_demand1)

bls_hh_demand1= bls_hh_demand1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_hh_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Germany, Households/ Demand for mortgage, full time series")+
  theme_bw()

```

### Germany, breakdown (Q2 2024)

```{r}

# Demand / House purchase: contributing factors to change in demand 
# Euro area

bls_hh_demand1<- bls_hh_demand1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.DE.ALL..H.H..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_hh_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_demand = date_convert(bls_hh_demand)

factors = c("Z","DR","RFR","IFS","LOB","OSF","GLI","HMP","CCF")

bls_hh_demand = bls_hh_demand  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Other financing needs" = sum(DR,RFR, na.rm = T)/2, 
         "Use of alternative finance" = sum(IFS, LOB, OSF, na.rm = T)/3, 
         "General Level of Interest Rate" = (GLI), 
         "Housing Market Prospects" = (HMP),
         "Consumer Confidence"=(CCF)) %>%
  select(-c("DR","RFR","IFS","LOB","OSF","GLI","HMP","CCF")) %>%
  gather(key = "bls_item", val = "value", -c("Z","time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_hh_demand,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_hh_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Germany, Households Credit standards, breakdown factors, full time series")

```


### Spain, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.ES.ALL.Z.H.H..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_hh_demand1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_demand1 = date_convert(bls_hh_demand1)

bls_hh_demand1= bls_hh_demand1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_hh_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Spain, Households/ Demand for mortgage, full time series")+
  theme_bw()

```

### Spain, breakdown (Q2 2024)

```{r}

# Demand / House purchase: contributing factors to change in demand 
# Euro area

bls_hh_demand1<- bls_hh_demand1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.ES.ALL..H.H..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_hh_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_demand = date_convert(bls_hh_demand)

factors = c("Z","DR","RFR","IFS","LOB","OSF","GLI","HMP","CCF")

bls_hh_demand = bls_hh_demand  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Other financing needs" = sum(DR,RFR, na.rm = T)/2, 
         "Use of alternative finance" = sum(IFS, LOB, OSF, na.rm = T)/3, 
         "General Level of Interest Rate" = (GLI), 
         "Housing Market Prospects" = (HMP),
         "Consumer Confidence"=(CCF)) %>%
  select(-c("DR","RFR","IFS","LOB","OSF","GLI","HMP","CCF")) %>%
  gather(key = "bls_item", val = "value", -c("Z","time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_hh_demand,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_hh_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Spain, Households Credit standards, breakdown factors, full time series")

```


### Italy, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.IT.ALL.Z.H.H..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_hh_demand1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_demand1 = date_convert(bls_hh_demand1)

bls_hh_demand1= bls_hh_demand1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_hh_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Italy, Households/ Demand for mortgage, full time series")+
  theme_bw()

```

### Italy, breakdown (Q2 2024)

```{r}

# Demand / House purchase: contributing factors to change in demand 
# Euro area

bls_hh_demand1<- bls_hh_demand1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.IT.ALL..H.H..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_hh_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_hh_demand = date_convert(bls_hh_demand)

factors = c("Z","DR","RFR","IFS","LOB","OSF","GLI","HMP","CCF")

bls_hh_demand = bls_hh_demand  %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Other financing needs" = sum(DR,RFR, na.rm = T)/2, 
         "Use of alternative finance" = sum(IFS, LOB, OSF, na.rm = T)/3, 
         "General Level of Interest Rate" = (GLI), 
         "Housing Market Prospects" = (HMP),
         "Consumer Confidence"=(CCF)) %>%
  select(-c("DR","RFR","IFS","LOB","OSF","GLI","HMP","CCF")) %>%
  gather(key = "bls_item", val = "value", -c("Z","time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_hh_demand,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_hh_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Italy, Households Credit standards, breakdown factors, full time series")

```

# BLS - Consumer 

## Section 3.1 Credit Standards 

### Euro Area, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.U2.ALL.Z.H.C..ST.S.WFNET"
df<- ecb::get_data(series_key)

bls_consumer_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_cstd1 = date_convert(bls_consumer_cstd1)

bls_consumer_cstd1= bls_consumer_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_consumer_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Euro Area, Consumer/ Credit standards, full time series")+
  theme_bw()

```

### Euro area, breakdown (Q2 2024)

```{r}

# CONSUMER CREDIT STANDARDS
# Euro Area, U2 

bls_consumer_cstd1<- bls_consumer_cstd1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.U2.ALL..H.C..ST.S.WFNET"
df<- ecb::get_data(series_key)

bls_consumer_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_cstd = date_convert(bls_consumer_cstd )

factors = c("Z","LP","MF","BSC","CP","GEA","RCD","CWC","NBC","BC","RTO")

bls_consumer_cstd = bls_consumer_cstd %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, BSC, CP, na.rm = T)/4, 
         "Risk perceptions" = sum(GEA, RCD, CWC, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, na.rm = T )/2, 
         "Banks' Risk tolerance" = (RTO)) %>%
  select(-c("LP","MF","BSC","CP","GEA","RCD","CWC","NBC","BC","RTO")) %>%
  gather(key = "bls_item", val = "value", -c("Z",  "time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_consumer_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_consumer_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Euro Area, Consumer Credit Standards, breakdown factors, full time series")

```


### Euro Area, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.U2.ALL.Z.H.C..ST.S.WFNET"
df<- ecb::get_data(series_key)

bls_consumer_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_cstd1 = date_convert(bls_consumer_cstd1)

bls_consumer_cstd1= bls_consumer_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_consumer_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Euro Area, Consumer/ Credit standards, full time series")+
  theme_bw()

```

### Euro area, breakdown (Q2 2024)

```{r}

# CONSUMER CREDIT STANDARDS
# Euro Area, U2 

bls_consumer_cstd1<- bls_consumer_cstd1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.U2.ALL..H.C..ST.S.WFNET"
df<- ecb::get_data(series_key)

bls_consumer_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_cstd = date_convert(bls_consumer_cstd )

factors = c("Z","LP","MF","BSC","CP","GEA","RCD","CWC","NBC","BC","RTO")

bls_consumer_cstd = bls_consumer_cstd %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, BSC, CP, na.rm = T)/4, 
         "Risk perceptions" = sum(GEA, RCD, CWC, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, na.rm = T )/2, 
         "Banks' Risk tolerance" = (RTO)) %>%
  select(-c("LP","MF","BSC","CP","GEA","RCD","CWC","NBC","BC","RTO")) %>%
  gather(key = "bls_item", val = "value", -c("Z",  "time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_consumer_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_consumer_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Euro Area, Consumer Credit Standards, breakdown factors, full time series")

```

### France, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.FR.ALL.Z.H.C..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_consumer_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_cstd1 = date_convert(bls_consumer_cstd1)

bls_consumer_cstd1= bls_consumer_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_consumer_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("France, Consumer/ Credit standards, full time series")+
  theme_bw()

```

### France, breakdown (Q2 2024)

```{r}

# CONSUMER CREDIT STANDARDS
# Euro Area, U2 

bls_consumer_cstd1<- bls_consumer_cstd1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.FR.ALL..H.C..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_consumer_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_cstd = date_convert(bls_consumer_cstd )

factors = c("Z","LP","MF","BSC","CP","GEA","RCD","CWC","NBC","BC","RTO")

bls_consumer_cstd = bls_consumer_cstd %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, BSC, CP, na.rm = T)/4, 
         "Risk perceptions" = sum(GEA, RCD, CWC, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, na.rm = T )/2, 
         "Banks' Risk tolerance" = (RTO)) %>%
  select(-c("LP","MF","BSC","CP","GEA","RCD","CWC","NBC","BC","RTO")) %>%
  gather(key = "bls_item", val = "value", -c("Z",  "time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_consumer_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_consumer_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("France, Consumer Credit Standards, breakdown factors, full time series")

```

### Germany, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.DE.ALL.Z.H.C..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_consumer_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_cstd1 = date_convert(bls_consumer_cstd1)

bls_consumer_cstd1= bls_consumer_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_consumer_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Germany, Consumer/ Credit standards, full time series")+
  theme_bw()

```

### Germany, breakdown (Q2 2024)

```{r}

# CONSUMER CREDIT STANDARDS
# Euro Area, U2 

bls_consumer_cstd1<- bls_consumer_cstd1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.DE.ALL..H.C..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_consumer_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_cstd = date_convert(bls_consumer_cstd )

factors = c("Z","LP","MF","BSC","CP","GEA","RCD","CWC","NBC","BC","RTO")

bls_consumer_cstd = bls_consumer_cstd %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, BSC, CP, na.rm = T)/4, 
         "Risk perceptions" = sum(GEA, RCD, CWC, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, na.rm = T )/2, 
         "Banks' Risk tolerance" = (RTO)) %>%
  select(-c("LP","MF","BSC","CP","GEA","RCD","CWC","NBC","BC","RTO")) %>%
  gather(key = "bls_item", val = "value", -c("Z",  "time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_consumer_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_consumer_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Germany, Consumer Credit Standards, breakdown factors, full time series")

```

### Spain, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.ES.ALL.Z.H.C..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_consumer_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_cstd1 = date_convert(bls_consumer_cstd1)

bls_consumer_cstd1= bls_consumer_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_consumer_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Spain, Consumer/ Credit standards, full time series")+
  theme_bw()

```

### Spain, breakdown (Q2 2024)

```{r}

# CONSUMER CREDIT STANDARDS
# Euro Area, U2 

bls_consumer_cstd1<- bls_consumer_cstd1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.ES.ALL..H.C..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_consumer_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_cstd = date_convert(bls_consumer_cstd )

factors = c("Z","LP","MF","BSC","CP","GEA","RCD","CWC","NBC","BC","RTO")

bls_consumer_cstd = bls_consumer_cstd %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, BSC, CP, na.rm = T)/4, 
         "Risk perceptions" = sum(GEA, RCD, CWC, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, na.rm = T )/2, 
         "Banks' Risk tolerance" = (RTO)) %>%
  select(-c("LP","MF","BSC","CP","GEA","RCD","CWC","NBC","BC","RTO")) %>%
  gather(key = "bls_item", val = "value", -c("Z",  "time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_consumer_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_consumer_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Spain, Consumer Credit Standards, breakdown factors, full time series")

```

### Italy, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.IT.ALL.Z.H.C..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_consumer_cstd1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_cstd1 = date_convert(bls_consumer_cstd1)

bls_consumer_cstd1= bls_consumer_cstd1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_consumer_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Italy, Consumer/ Credit standards, full time series")+
  theme_bw()

```

### Italy, breakdown (Q2 2024)

```{r}

# CONSUMER CREDIT STANDARDS
# Euro Area, U2 

bls_consumer_cstd1<- bls_consumer_cstd1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.IT.ALL..H.C..ST.S.FNET"
df<- ecb::get_data(series_key)

bls_consumer_cstd = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_cstd = date_convert(bls_consumer_cstd )

factors = c("Z","LP","MF","BSC","CP","GEA","RCD","CWC","NBC","BC","RTO")

bls_consumer_cstd = bls_consumer_cstd %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Cost of funds and balance sheet constraints" = sum(LP, MF, BSC, CP, na.rm = T)/4, 
         "Risk perceptions" = sum(GEA, RCD, CWC, na.rm = T)/3, 
         "Competition" = sum(NBC, BC, na.rm = T )/2, 
         "Banks' Risk tolerance" = (RTO)) %>%
  select(-c("LP","MF","BSC","CP","GEA","RCD","CWC","NBC","BC","RTO")) %>%
  gather(key = "bls_item", val = "value", -c("Z",  "time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_consumer_cstd,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_consumer_cstd1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Italy, Consumer Credit Standards, breakdown factors, full time series")

```

## Section 3.2 Demand

### Euro area, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.U2.ALL.Z.H.C..ZZ.D.WFNET"
df<- ecb::get_data(series_key)

bls_consumer_demand1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_demand1 = date_convert(bls_consumer_demand1)

bls_consumer_demand1= bls_consumer_demand1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_consumer_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Euro Area, Consumer/ Demand, full time series")+
  theme_bw()

```

### Euro Area, breakdown (Q2 2024)

```{r}

# Demand / Consumer: contributing factors to change in demand 
# Euro area

bls_consumer_demand1<- bls_consumer_demand1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.U2.ALL..H.C..ZZ.D.WFNET"
df<- ecb::get_data(series_key)

bls_consumer_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_demand = date_convert(bls_consumer_demand)

factors = c("Z","SDC","IFS","LOB","OSF","GLI","CRE","CCF")

bls_consumer_demand = bls_consumer_demand %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Spending on durable goods" = (SDC),
         "Use of alternative finance" = sum(IFS, LOB, OSF, na.rm = T)/3, 
         "General Level of Interest Rate" = (GLI), 
         "Consumption exp.(real estate)" = (CRE),
         "Consumer Confidence"=(CCF)) %>%
  select(-c("SDC","IFS","LOB","OSF","GLI","CRE","CCF")) %>%
  gather(key = "bls_item", val = "value", -c("Z","time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_consumer_demand,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_consumer_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Euro Area, Consumer/Demand, breakdown factors, full time series")

```

### France, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.FR.ALL.Z.H.C..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_consumer_demand1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_demand1 = date_convert(bls_consumer_demand1)

bls_consumer_demand1= bls_consumer_demand1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_consumer_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("France, Consumer/ Demand, full time series")+
  theme_bw()

```

### France, breakdown (Q2 2024)

```{r}

# Demand / Consumer: contributing factors to change in demand 
# Euro area

bls_consumer_demand1<- bls_consumer_demand1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.FR.ALL..H.C..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_consumer_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_demand = date_convert(bls_consumer_demand)

factors = c("Z","SDC","IFS","LOB","OSF","GLI","CRE","CCF")

bls_consumer_demand = bls_consumer_demand %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Spending on durable goods" = (SDC),
         "Use of alternative finance" = sum(IFS, LOB, OSF, na.rm = T)/3, 
         "General Level of Interest Rate" = (GLI), 
         "Consumption exp.(real estate)" = (CRE),
         "Consumer Confidence"=(CCF)) %>%
  select(-c("SDC","IFS","LOB","OSF","GLI","CRE","CCF")) %>%
  gather(key = "bls_item", val = "value", -c("Z","time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_consumer_demand,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_consumer_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("France, Consumer/Demand, breakdown factors, full time series")

```

### Germany, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.DE.ALL.Z.H.C..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_consumer_demand1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_demand1 = date_convert(bls_consumer_demand1)

bls_consumer_demand1= bls_consumer_demand1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_consumer_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Germany, Consumer/ Demand, full time series")+
  theme_bw()

```

### Germany, breakdown (Q2 2024)

```{r}

# Demand / Consumer: contributing factors to change in demand 
# Euro area

bls_consumer_demand1<- bls_consumer_demand1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.DE.ALL..H.C..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_consumer_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_demand = date_convert(bls_consumer_demand)

factors = c("Z","SDC","IFS","LOB","OSF","GLI","CRE","CCF")

bls_consumer_demand = bls_consumer_demand %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Spending on durable goods" = (SDC),
         "Use of alternative finance" = sum(IFS, LOB, OSF, na.rm = T)/3, 
         "General Level of Interest Rate" = (GLI), 
         "Consumption exp.(real estate)" = (CRE),
         "Consumer Confidence"=(CCF)) %>%
  select(-c("SDC","IFS","LOB","OSF","GLI","CRE","CCF")) %>%
  gather(key = "bls_item", val = "value", -c("Z","time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_consumer_demand,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_consumer_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Germany, Consumer/Demand, breakdown factors, full time series")

```

### Spain, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.ES.ALL.Z.H.C..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_consumer_demand1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_demand1 = date_convert(bls_consumer_demand1)

bls_consumer_demand1= bls_consumer_demand1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_consumer_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("Spain, Consumer/ Demand, full time series")+
  theme_bw()

```

### Spain, breakdown (Q2 2024)

```{r}

# Demand / Consumer: contributing factors to change in demand 
# Euro area

bls_consumer_demand1<- bls_consumer_demand1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.ES.ALL..H.C..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_consumer_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_demand = date_convert(bls_consumer_demand)

factors = c("Z","SDC","IFS","LOB","OSF","GLI","CRE","CCF")

bls_consumer_demand = bls_consumer_demand %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Spending on durable goods" = (SDC),
         "Use of alternative finance" = sum(IFS, LOB, OSF, na.rm = T)/3, 
         "General Level of Interest Rate" = (GLI), 
         "Consumption exp.(real estate)" = (CRE),
         "Consumer Confidence"=(CCF)) %>%
  select(-c("SDC","IFS","LOB","OSF","GLI","CRE","CCF")) %>%
  gather(key = "bls_item", val = "value", -c("Z","time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_consumer_demand,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_consumer_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Spain, Consumer/Demand,breakdown factors, full time series")

```

### Italy, full series (Q2 2024)

```{r}

series_key <- "BLS.Q.IT.ALL.Z.H.C..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_consumer_demand1 = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_demand1 = date_convert(bls_consumer_demand1)

bls_consumer_demand1= bls_consumer_demand1%>%
  mutate(Date=date-months(3))%>%
  mutate(ReferenceHorizon=case_when(
    time_horizon=="B3"~"Backward Looking",
    time_horizon=="F3"~"Forward Looking"
  ))%>%
  select(Date,ReferenceHorizon,obsvalue)

ggplot(data=bls_consumer_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon))+
  geom_line(aes(color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  ggtitle("France, Consumer/ Demand, full time series")+
  theme_bw()

```

### Italy, breakdown (Q2 2024)

```{r}

# Demand / Consumer: contributing factors to change in demand 
# Euro area

bls_consumer_demand1<- bls_consumer_demand1%>%
  filter(Date>="2020-01-01")

series_key <- "BLS.Q.IT.ALL..H.C..ZZ.D.FNET"
df<- ecb::get_data(series_key)

bls_consumer_demand = df[, c("obstime", "obsvalue", "bls_item", "time_horizon")]

bls_consumer_demand = date_convert(bls_consumer_demand)

factors = c("Z","SDC","IFS","LOB","OSF","GLI","CRE","CCF")

bls_consumer_demand = bls_consumer_demand %>%
  filter(bls_item %in% factors) %>%
  spread(bls_item, obsvalue) %>%
  rowwise() %>%
  mutate("Spending on durable goods" = (SDC),
         "Use of alternative finance" = sum(IFS, LOB, OSF, na.rm = T)/3, 
         "General Level of Interest Rate" = (GLI), 
         "Consumption exp.(real estate)" = (CRE),
         "Consumer Confidence"=(CCF)) %>%
  select(-c("SDC","IFS","LOB","OSF","GLI","CRE","CCF")) %>%
  gather(key = "bls_item", val = "value", -c("Z","time_horizon", "date", "obstime")) %>%
  group_by(bls_item) %>%
  mutate(Date = date - months(3))%>%
  mutate(Factors=bls_item)%>%
  filter(Date>="2020-01-01")

ggplot()+
  geom_bar(data=bls_consumer_demand,aes(x=Date,y=value,fill=Factors,group=Factors),stat="Identity")+
  geom_line(data=bls_consumer_demand1,aes(x=Date,y=obsvalue,group=ReferenceHorizon,color=ReferenceHorizon))+
  scale_color_manual(values=c("red","black"))+
  labs(x="Date",y="Net Percentage")+
  theme_bw()+
  ggtitle("Italy, Consumer/Demand, breakdown factors, full time series")

```

